---
title: "A UN Report on the Relationship between GDP and Life Expectancy and CO2 emissions"
author: "Katrina"
date: "1/18/2023"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r load-packages}
library(tidyverse)
```

This report was prepared to the attention of the United Nations. It analyzes the relationship between a country's GDP, its life expectancy and CO2 emissions. Our goal is to determine to what degree a country’s economic strength or weakness may be related to its public health status and impact on climate pollution. We hypothesize that both life expectancy and CO2 emissions increase with a country's GDP.

```{r read-data}
gapminder_1997 <- read_csv("code/gapminder_1997.csv")
```

```{r gdp -lifeExp-1997-plot}
# make plot of GDP (x-axis) vs LifeExp (y-axis)
ggplot(gapminder_1997) +
  (aes(x = gdpPercap, y = lifeExp)) +
  geom_point() +
  theme_classic() +
  labs(x= "GDP", y = "LifeExp (in years)", title = "Comparing GDP versus Life Expectancy")
```

